Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-13 paper/paper.qmd
Added Figures

# Read data
cleaned_test_score_data <- read_csv(here("data/analysis_data/cleaned_test_score_data.csv"))
cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv"))
```

@@

>>>>

# Read data
cleaned_test_score_data <- read_csv(here("data/analysis_data/cleaned_test_score_data.csv"))
cleaned_region_data <- read_csv(here("data/analysis_data/cleaned_region_data.csv"))

averaged_broadband <- read_csv(here("data/analysis_data/averaged_broadband.csv"))
```

@@

```{r}
#| label: fig-broadband
#| echo: false
#| fig-cap: "BroadBand"
library(tidyverse)
library(janitor)
library(dplyr)
library(knitr)
library(here)
library(readxl)
library(ggplot2)

ggplot(averaged_broadband, aes(x = QUANTILE_LABEL, y = average)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(x = "Quantile Label", y = "Average") +
  ggtitle("Average Days Virtual by Quantile") +
  geom_text(aes(label = sprintf("%.0f", average)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, size = 3) +
  labs(x = "Quantile", y = "Average Days Virtual") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```
